Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-09-07 paper/paper.tex
Work in progress to add receptor-ligand AND receptor-receptor interactions

% Define title, empty date and authors
\title {
  Competition can account for stopping in a gradient-following model
  of the retinotectal projection \\
  \emph{or} \\
  Competition provides stopping for the chemoaffinity
  theory which is robust to noise \\
  \emph{or} \\
  Self-organisation of topographically ordered axon connections can take place
  in a noisy environment if axons compete \\
  \emph{or} \\
  Time to stop; modelling chemoaffinity with competition \\
  \emph{or} \\
  Can the retinotectal projection be modelled exclusively by receptor-ligand interactions?
}
\date{} % No date please
\author{\Authors}

>>>>

% Define title, empty date and authors
\title {
%  Competition can account for stopping in a gradient-following model
%  of the retinotectal projection \\
%  \emph{or} \\
%  Competition provides stopping for the chemoaffinity
%  theory which is robust to noise \\
%  \emph{or} \\
%  Self-organisation of topographically ordered axon connections can take place
%  in a noisy environment if axons compete \\
%  \emph{or} \\
  Time to stop; agent-based modelling of chemoaffinity with competition
}
\date{} % No date please
\author{\Authors}
